Overrelaxed Sinkhorn--Knopp Algorithm for Regularized Optimal Transport

### 2017-11-20 PosterNIPS2017.tex
Poster

\documentclass[portrait,a0paper,fontscale=0.35]{baposter} % Adjust the font scale/size here : fontscale=0.285
\usepackage{textpos}
\usepackage[frenchb]{babel}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{tikz}
\usepackage{graphicx} % Required for including images
%\graphicspath{{Figures/}} % Directory in which figures are stored
\usepackage{amsmath} % For typesetting math
\usepackage{amsthm}
\usepackage{amssymb} % Adds new symbols to be used in math mode
\usepackage{booktabs} % Top and bottom rules for tables
\usepackage{enumitem} % Used to reduce itemize/enumerate spacing
\usepackage{palatino} % Use the Palatino font
\usepackage[font=small,labelfont=bf]{caption} % Required for specifying captions to tables and figures
\usepackage{multicol} % Required for multiple columns
\usepackage{tikz} % Required for flow chart
\usetikzlibrary{shapes,arrows} % Tikz libraries required for the flow chart in the template
\usepackage{dsfont}
\usepackage{listings}
\usepackage{subfigure}
\usepackage{color}
\usepackage{nth}
\usepackage{a4wide}
\usepackage{graphicx,color}
\usepackage{array}
\usepackage[nottoc, notlof, notlot]{tocbibind}
\usepackage{subfigure}
\usetikzlibrary{arrows,shapes,positioning,calc}
%\definecolor{CPU}{RGB}{30, 167, 223}
%\definecolor{CPU}{RGB}{8, 138, 104}
\definecolor{gris}{gray}{0.9}
\usepackage{geometry}
\geometry{left=0.5cm,right=0.5cm,bottom=0.5cm,top=0.5cm,centering}
\usepackage{subfig}
\usepackage{float}
\usepackage{multicol}
\usepackage{enumitem,rotating}
\usepackage{bbm}
\usepackage{wrapfig}

@@

\headerbox{Introduction}{name=intro,column=0}{
	Optimal Transport is an efficient and flexible tool to compare two probability distributions. It has been popularized in the computer vision community in the context of discrete histograms \cite{Rubner2000}. The introduction of entropic regularization in \cite{cuturi13} has made possible the use of the fast Sinkhorn--Knopp algorithm \cite{sinkhorn64} scaling with high dimensional data.\\
	\begin{minipage}{0.49\textwidth}
	\begin{center}
		\includegraphics[width=5cm]{schema_c}
	\end{center}
	\caption{A wrapped figure going nicely inside the text.}\label{wrap-fig:1}
	\end{minipage}
	\begin{minipage}{0.49\textwidth}
		Optimal Transport is an efficient and flexible tool to compare two probability distributions. It has been popularized in the computer vision community in the context of discrete histograms \cite{Rubner2000}. The introduction of entropic regularization in \cite{cuturi13} has made possible the use of the fast Sinkhorn--Knopp algorithm \cite{sinkhorn64} scaling with high dimensional data.
	\end{minipage}
}

@@

\headerbox{Sinkhorn-Knopp Algorithm}{name=Sinkhorn,column=0,below=intro}{
	We aim at numerically solving the entropic regularization of optimal transport~:
	\begin{equation} \label{eq:problem}
	\gamma^* = \argmin_{\gamma \in \Ccal_1 \cap \Ccal_2}
	\scal{c}{\gamma} + \epsilon \KL(\gamma,\One)
	\end{equation}
}

>>>>

\documentclass[portrait,a0paper,fontscale=0.35]{baposter} % Adjust the font scale/size here : fontscale=0.285
%\usepackage{textpos}
\usepackage[frenchb]{babel}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{tikz}
\usepackage{graphicx} % Required for including images
%\graphicspath{{Figures/}} % Directory in which figures are stored
\usepackage{amsmath} % For typesetting math
\usepackage{amsthm}
\usepackage{amssymb} % Adds new symbols to be used in math mode
\usepackage{booktabs} % Top and bottom rules for tables
\usepackage{enumitem} % Used to reduce itemize/enumerate spacing
\usepackage{palatino} % Use the Palatino font
\usepackage[font=small,labelfont=bf]{caption} % Required for specifying captions to tables and figures
\usepackage{multicol} % Required for multiple columns
\usepackage{tikz} % Required for flow chart
\usetikzlibrary{shapes,arrows} % Tikz libraries required for the flow chart in the template
%\usepackage{dsfont}
%\usepackage{listings}
\usepackage{subfigure}
\usepackage{color}
%\usepackage{nth}
%\usepackage{a4wide}
\usepackage{graphicx,color}
\usepackage{array}
%\usepackage[nottoc, notlof, notlot]{tocbibind}
\usepackage{subfigure}
\usetikzlibrary{arrows,shapes,positioning,calc}
%\definecolor{CPU}{RGB}{30, 167, 223}
%\definecolor{CPU}{RGB}{8, 138, 104}
\definecolor{gris}{gray}{0.9}
\usepackage{geometry}
\geometry{left=0.5cm,right=0.5cm,bottom=0.5cm,top=0.5cm,centering}
%\usepackage{subfig}
\usepackage{float}
\usepackage{multicol}
\usepackage{enumitem,rotating}
\usepackage{bbm}
%\usepackage{wrapfig}

@@

\headerbox{Introduction}{name=intro,column=0}{
	Optimal Transport is an efficient and flexible tool to compare two probability distributions. It has been popularized in the computer vision community in the context of discrete histograms [Rubner, 2000]. The introduction of entropic regularization in [Cuturi, 2013] has made possible the use of the fast Sinkhorn--Knopp algorithm (SK) [Sinkhorn, 1964c] scaling with high dimensional data.\\
	\begin{center}
		\begin{tabular}{c c c c}
		\includegraphics[height=3cm]{1d_interp_mu} &
		\includegraphics[height=3cm]{1d_interp_0_2} &
		\includegraphics[height=3cm]{1d_interp_2} &
		\includegraphics[height=3cm]{1d_interp_18} \\
		&
		$\epsilon = 5$ &
		$\epsilon = 0.5$ &
		$\epsilon = 0.02$
		\end{tabular}
	\captionof{figure}{Regularized optimal transport maps for decreasing regularization parameter $\epsilon$.}
	\end{center}
	For small regularization $\epsilon$, the SK algorithm becomes extremely slow. To counter this, we propose a new algorithm that accelerates SK by \emph{overrelaxation}.
}

@@

\headerbox{Sinkhorn-Knopp Algorithm}{name=Sinkhorn,column=0,below=intro}{
	We aim at numerically solving the entropic regularization of optimal transport:
	\begin{equation} \label{eq:problem}
	\gamma^* = \argmin_{\gamma \in \Ccal_1 \cap \Ccal_2}
	\scal{c}{\gamma} + \epsilon \KL(\gamma,\One).
	\end{equation}
	In this equation, $\Ccal_1$ and $\Ccal_2$ are the marginal constraint sets corresponding to two discrete measures $\mu^1$ and $\mu^2$,
	and where $\KL$ is the Kullback--Leibler divergence.
	\begin{gather*}
	\Ccal_1 = \left\{ \gamma \mid A_1 \gamma = \mu^1 \right\},
	\quad\quad\quad
	\Ccal_2 = \left\{ \gamma \mid A_2 \gamma = \mu^2 \right\}.\\
	\KL(\gamma,\xi) = \sum_{i,j} \gamma_{i,j} \left( \log \left( \frac{\gamma_{i,j}}{\xi_{i,j}} \right) -1  \right) + \sum_{i,j} \xi_{i,j}.
	\end{gather*}
	As it is strictly convex, it has exactly one solution. It can be written equivalently as the \emph{Bregman projection} of a point onto a convex set:
	\begin{gather*}
	P_{\Ccal}(\xi) := \argmin_{\gamma \in \Ccal} \KL(\gamma,\xi),\\
	\gamma^* = P_{\Ccal_1 \cap \Ccal_2}(e^{-c/\epsilon}).
	\end{gather*}
	Whereas projecting onto $\Ccal_1 \cap \Ccal_2$ is challenging, projecting onto $\Ccal_1$ or $\Ccal_2$ individually is much easier: indeed, it corresponds to scaling the rows or columns of the matrix so that the corresponding marginal sum is correct.
	Therefore the solution can be computed by alternating Bregman projections, as shown in [Bregman, 1964]:
	\[
	\lim P_{\Ccal_2}\circ P_{\Ccal_1} \circ \ldots \circ P_{\Ccal_2} \circ P_{\Ccal_1} (\gamma^0) = \gamma^*
	\]
}
